Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
first draft of data section; added more references and outline

Here we present a new set of full-sky coadds generated by
combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
programs. These `full-depth' coadds are publicly available 
online\footnote{http://unwise.me}. In $\S$1 we briefly describe the W1/W2 
single-exposure data set on which our full-depth coadds are based. In $\S$2
we describe an empirical, custom photometric calibration we derived in order 
to combine pre and post reactivation WISE images. In $\S$3 we describe our
rejection of time-dependent artifacts, particularly off-axis Moon 
contamination. In $\S$4 we describe our strategy for recovering 
Moon-contaminated exposures. In $\S$5 we highlight some important aspects 
of the full-sky set of full-depth coadds generated by our processing. In 
$\S$6, we present a preliminary investigation of the improvements in WISE 
depth which have resulted from doubling the amount of W1/W2 imaging. We 
conclude in $\S$7 with a brief discussion of future uses of our present 
WISE+NEOWISER coadds, as well as remaining work to be done with existing and 
future NEOWISER imaging.

% mention DECaLS in intro and add footnote to legacysurvey website

%In the remainder of this proposal, we will refer to the data from the
%first 13 months of the mission as simply ``WISE'', in contrast to
%data from the current ``NEOWISER'' mission phase.

@@

>>>>

Here we present a new set of full-sky coadds generated by
combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
programs. These `full-depth' coadds are publicly available 
online\footnote{http://unwise.me}. In $\S$\ref{sec:data} we briefly describe 
the W1/W2 single-exposure data set on which our full-depth coadds are based. 
In $\S$\ref{sec:calib} we describe an empirical, custom photometric calibration
we derived in order to combine pre and post reactivation WISE images. In 
$\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
particularly off-axis Moon contamination. In $\S$\ref{sec:recover} we describe
our strategy for recovering Moon-contaminated exposures. In 
$\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
of full-depth coadds generated by our processing. In $\S$\ref{sec:depth}, we 
present a preliminary investigation of the improvements in WISE depth which 
have resulted from doubling the amount of W1/W2 imaging. We conclude in 
$\S$\ref{sec:future} with a brief discussion of future uses of our present 
WISE+NEOWISER coadds, as well as remaining work to be done with existing and 
future NEOWISER imaging.

\section{Data}
\label{sec:data}

The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images form the basis
for our W1/W2 coadds. Specifically, for each L1b frameset, we make use of the 
per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, which respectively
give the measured sky intensity and associated per-pixel bitmask values and 
uncertainty estimates. We have obtained a local copy of these files for every 
W1 and W2 frameset, including those from the AllWISE release ($\sim$2.9M 
framesets) and first-year NEOWISER release ($\sim$2.5M framesets). In
total we have analyzed $\sim$5.4M framesets in each of W1 and W2, corresponding
to a total of $\sim$32M L1b image files and $\sim$71TB of pixel data.

In addition to L1b images, we also make use of several official WISE
catalog-level data products. During the photometric calibration described
in $\S$\ref{sec:calib}, we select sources to photometer based on the AllWISE 
Source Catalog \citep{cutri13}. Also, to flag and reject bright solar system 
planets ($\S$\ref{sec:moon}), we make use of the WISE Known Solar System Object
Possible Association List for each mission phase 
\citep{cutri12, cutri13,cutri15}.

% mention that we use the allwise source catalog during the photometric
% mention that we also use the various ``known solar system possible 
% association list'' catalogs

\section{Custom Photometric Calibration}
\label{sec:calib}

\section{Removing Time-dependent Artifacts}
\label{sec:moon}

\section{Recovering Contaminated Frames}
\label{sec:recover}

\section{Overview of Results}
\label{sec:results}

\section{Preliminary Depth Characterization}
\label{sec:depth}

\section{Conclusion \& Future Work}
\label{sec:future}

% add footnote to legacysurvey website in section that compares
% wise depths in DECaLS DR1 versus DR2

@@

% cite software packages such as numpy, scipy, matplotlib ??
